\section{bx\_muon\_decoder}

This module performs the decoding of muon data. It requires the muon part of the event to be in the raw stage.
It is friend of the \code{bx\_muon\_decoded\_event} and \code{bx\_muon\_decoded\_hit} class.
At the end of the work the muon event is marked into \code{decoded} stage.

Currently neutrino trgtypes and laser394 trgtypes are handled by two indipendent helper methods:
\begin{enumerate}
\item \code{m\_process\_physics\_event()}
\item \code{m\_process\_laser\_event()}
\end{enumerate}
All other trigger types are discarded with a warning level message.

Possibly the laser event processing will be moved to a dedicated calibration module.

\subsection{physics}

Time is evaluated to TDC gate opening (1 << 13 ticks before trigger), in nanoseconds\footnote{through constant \code{constants::muon::tdc::ns\_per\_clock}}.
Correction for PMT time offset is not yet applied since calibration are not yet completed.
Hits outside the gate (improbable) are discarded.

Charge is evaluated as the TDC time difference (lead-trail), pedestal subtracted, and currently converted in pe with constants measured for 1 QTC channel.
As soon as calibrations will be completed, this will be changed accordingly.

\subsection{laser}

A first quick loop on hits finds the reference channel.
If this is not found the method return with an error level message. 

Time is evaluated as time from LED reference pulse, in nanoseconds\footnote{through constant \code{constants::muon::tdc::ns\_per\_clock}}.
Hits coming before reference pulse are discarded (as well as improbable out of gate hits).

Charge is evaluated as the TDC time difference (lead-trail), pedestal subtracted, and currently converted in pe with constants measured for 1 QTC channel.
The charge calibration strategy is still to be defined
